Proposal: Studying How Baseball Players Perform After Signing A New Contract

### 2022-11-14 proposal/proposal.tex
Update proposal.tex
fix

\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}

@@

\paragraph{Specific Aims}
My research hypothesis will be as follows: Major league baseball players see a decline in performance after switching teams in free agency when compared with players that re-sign a new contract with their current team. This hypothesis tests a long-posited theory that teams who sign new players don’t always get the player they bargained for. The concept is extremely relevant because teams rely on free agency to build the nucleus of their teams. Per Spotrac, over $3 billion in new contracts were signed in the last baseball offseason, signifying the importance of calculated and sound free agency decisions by both players and teams.

@@

\bibliography{course-paper-or-presentation/PROPOSAL/citations.bib}
\bibliographystyle{chicago}

>>>>

\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}

@@

\paragraph{Specific Aims}
My research hypothesis will be as follows: Major league baseball players see a decline in performance after switching teams in free agency when compared with players that re-sign a new contract with their current team. This hypothesis tests a long-posited theory that teams who sign new players don’t always get the player they bargained for. The concept is extremely relevant because teams rely on free agency to build the nucleus of their teams. Per Spotrac, over 3 billion dollars in new contracts were signed in the last baseball offseason, signifying the importance of calculated and sound free agency decisions by both players and teams.

@@

\bibliography{course-paper-or-presentation-jasonboghosian/proposal/citations.bib}
\bibliographystyle{chicago}
